---
title: United Nations Votes
subtitle: My first Quarto file
author: Anmol Virdi
format: pdf
date: today
---

# Introduction

How do various countries vote in the United Nations General Assembly, how have their voting patterns evolved throughout time, and how similarly or differently do they view certain issues? Answering these questions (at a high level) is the focus of this analysis.

## Packages

We will use the **tidyverse**, **lubridate**, and **scales** packages for data wrangling and visualization, and the **DT** package for interactive display of tabular output, and the **unvotes** package for the data.

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(lubridate)
library(scales)
library(DT)
library(unvotes)
```

## Data

The data we're using originally come from the **unvotes** package. In the chunk below we modify the data by joining the various data frames provided in the package to help you get started with the analysis.

```{r}
unv <- unvotes::un_votes %>%
  inner_join(un_roll_calls, by = "rcid") %>%
  inner_join(un_roll_call_issues, by = "rcid")
```

# UN voting patterns

Let's create a data visualisation that displays how the voting record of the UK & NI changed over time on a variety of issues, and compares it to two other countries: US and Turkey.

```{r}
#| label: plot-yearly-yes-issue
#| fig-width: 10
#| fig-height: 6

unv %>%
  filter(country %in% c("United Kingdom", "United States", "Turkey")) %>%
  mutate(year = year(date)) %>%
  group_by(country, year, issue) %>%
  summarize(percent_yes = mean(vote == "yes")) %>%
  ggplot(mapping = aes(x = year, y = percent_yes, color = country)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~issue) +
  scale_y_continuous(labels = percent) +
  labs(
    title = "Percentage of 'Yes' votes in the UN General Assembly",
    subtitle = "1946 to 2019",
    y = "% Yes",
    x = "Year",
    color = "Country"
  )
```

**1. Write 1-2 sentences here about what you learned from these plots**

Issues around conflicts could be rising. The trends in colonialism, nuclear weapons, economic dev.

Some countries have a general increase in trend, some decrease, the direction of the lines are generall going upward from fleft to right, ending higher/lower than started.

All three countries were alligned except colonialism & palestine conflict - the lines end very far at the end, and the lines diverge over time.

We can easily change which countries are being plotted by changing which countries the code above `filter`s for. Note that the country name should be spelled and capitalized exactly the same way as it appears in the data. See the [Appendix](#appendix) for a list of the countries in the data.

**2. Customize the plot** Choose different countries to explore. Copy the entire code chunk from above to below this line, edit the countries and re-render. Write a few sentences comparing these countries to the ones above.

```{r}
#| label: plot-yearly-no-issue
#| fig-width: 10
#| fig-height: 6

unv %>%
  filter(country %in% c("Spain", "Russia", "China")) %>%
  mutate(year = year(date)) %>%
  group_by(country, year, issue) %>%
  summarize(percent_yes = mean(vote == "yes")) %>%
  ggplot(mapping = aes(x = year, y = percent_yes, color = country)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~issue) +
  scale_y_continuous(labels = percent) +
  labs(
    title = "Percentage of 'Yes' votes in the UN General Assembly",
    subtitle = "1946 to 2019",
    y = "% Yes",
    x = "Year",
    color = "Country"
  )
```

Human rights reached close to 75% for all three countries

Nuclear weapons and material seem to be decreasing for all countries.

Economic development decreasing for the 3 countries.

## References

1.  David Robinson (2017). [unvotes](https://CRAN.R-project.org/package=unvotes): United Nations General Assembly Voting Data. R package version 0.2.0.
2.  Erik Voeten "Data and Analyses of Voting in the UN General Assembly" Routledge Handbook of International Organization, edited by Bob Reinalda (published May 27, 2013).
3.  Much of the analysis has been modeled on the examples presented in the [unvotes package vignette](https://cran.r-project.org/web/packages/unvotes/vignettes/unvotes.html).
